### 2015-03-01 paper_10_intro.tex
minor changes around the acronym SDO uploaded new output PDF file
some minor typos and proof reading

    Software development organizations need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The Cumulative Result Indicator (CRI)
    framework provides a solid foundation
    for a consistent evaluation.  CRI analyzes the historical performance
    of an SDO
    to create a baseline in order to provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus soley on the source code
    being produced.  However, a software development organization does more
    than just produce source code.  There is documentation to be
    written, testcases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall software development organization, not just the
    source code.

@@

    Software quality is one of the most well studied aspects
    of software development.  Most of the work focuses on
    either the problems with the software or the source code.
    Quality and the number of problems with the software
    are inversely related, more problems means lower quality. 
    Quality is easy to measure, but 
    that measurement is usually very software specific.  It is easy
    to find that some software has $X$ number of problems, but
    it is nearly impossible to determine whether the quality
    of that software is better or worse than some other software
    with $X$ defects.  One piece of software can be 
    larger\footnote{Saying a piece of software is larger can be a 
    rather arbitrary statement.  Does that mean the software requires 
    more computing time, has more lines of code, more documentation, 
    more hours spent on development, or some other arbitrary measure.}
    or more complex.  Thus, finding a value for quality is easier 
    than interpreting that value.  No matter the interpretation,
    the goal is to release the number of problems with the software.
    Top 10 lists have been created for techniques to remove problems
    from software \cite{Boehm2001}.  
    A number of different techniques or best practices
    for preventing defects have 
    been proposed \cite{Faizan2012}.  These are all strategies to identify
    or remove the problems before the software is completed and released
    to users.

>>>>

    Software development organizations need a framework to define
    what measurements should be tracked and how those measurements
    should be reported.  The Cumulative Result Indicator (CRI)
    framework provides a solid foundation
    for a consistent evaluation.  CRI analyzes the historical performance
    of a Software Development Organization (SDO)
    to create a baseline in order to provide a broad
    view of the overall organization.  It is common for software development
    organizations to measure and focus soley on the source code
    being produced.  However, a software development organization does more
    than just produce source code.  There is documentation to be
    written, testcases to be created, systems to be deployed, and
    decisions to be made.  The framework provides an evaluation
    of the overall software development organization, not just the
    source code.

@@

    Software quality is one of the most well studied aspects
    of software development.  Most of the work focuses on
    either the problems with the software or the source code.
    Quality and the number of problems with the software
    are inversely related, more problems means lower quality. 
    Quality is easy to measure, but 
    that measurement is usually very software specific.  It is easy
    to find that some software has $X$ number of problems, but
    it is nearly impossible to determine whether the quality
    of that software is better or worse than some other software
    with $X$ defects.  One piece of software can be 
    larger\footnote{Saying a piece of software is larger can be a 
    rather arbitrary statement.  It can mean the software requires 
    more computing time, has more lines of code, more documentation, 
    more hours spent on development, or some other arbitrary measure.}
    or more complex.  Thus, finding a value for quality is easier 
    than interpreting that value.  No matter the interpretation,
    the goal is to release the number of problems with the software.
    Top 10 lists have been created for techniques to remove problems
    from software \cite{Boehm2001}.  
    A number of different techniques or best practices
    for preventing defects have 
    been proposed \cite{Faizan2012}.  These are all strategies to identify
    or remove the problems before the software is completed and released
    to users.

### 2015-03-01 paper_30_measure.tex
some minor typos and proof reading

            Antolic in \cite{Antolic2008} made one of the earliest attempts
            to identify and measure the KPIs for an SDO. Antolic's strategy
            focused around 7 KPIs.
            \begin{enumerate}
                \item Schedule Adherence
                \item Assigned Content Adherence
                \item Cost Adherence
                \item Fault slip through
                \item Trouble report closure rate
                \item Cost per defect
            \end{enumerate}
            However, according to the definition of KPI just presented,
            they are not really KPIs but instead KRIs.  That is because
            none of the 7 clearly indicate the action required to 
            improve the measure.  Also, it is unclear if improving any of
            the measures will drastically improve performance.

@@

        In 2010, David Parmenter \cite{parmenter2010} added 2 more
        characteristics to the balanced scorecard: employee satisfaction
        and environment/community.  This results in a total of 6 
        characteristics for the balanced scorecard.
        \begin{enumerate}
          \item Financial 
          \item Customer Focus
          \item Internal Process
          \item Learning and Growth
          \item Employee Satisfaction\footnote{\label{ft:bsc} These 2 
                characteristics are not a part of the original balanced 
                scorecard presented by Kaplan and Norton in 1992.  
                They  were added later by Parmenter \cite{parmenter2010}. }
          \item Environment/Community\textsuperscript{\ref{ft:bsc}}
        \end{enumerate}

>>>>

            Antolic in \cite{Antolic2008} made one of the earliest attempts
            to identify and measure the KPIs for an SDO. Antolic's strategy
            focused around 7 KPIs.
            \begin{enumerate}
                \item Schedule adherence
                \item Assigned content adherence
                \item Cost adherence
                \item Fault slip through
                \item Trouble report closure rate
                \item Cost per defect
            \end{enumerate}
            However, according to the definition of KPI just presented,
            they are not really KPIs but instead KRIs.  That is because
            none of the 7 clearly indicate the action required to 
            improve the measure.  Also, it is unclear if improving any of
            the measures will drastically improve performance.

@@

        In 2010, David Parmenter \cite{parmenter2010} added 2 more
        characteristics to the balanced scorecard: employee satisfaction
        and environment/community.  This results in a total of 6 
        characteristics for the balanced scorecard.
        \begin{enumerate}
          \item Financial 
          \item Customer Focus
          \item Internal Process
          \item Learning and Growth
          \item Employee Satisfaction\footnote{\label{ft:bsc} Added 
          later by Parmenter \cite{parmenter2010}. }
          \item Environment/Community\textsuperscript{\ref{ft:bsc}}
        \end{enumerate}

### 2015-03-01 paper_40_cri.tex
some minor typos and proof reading

    As long as those 5 features are met, the range can be anything.  
    The range of $[-1,1]$ was chosen because it is easy to scale 
    to a different range such as $[-10,10]$ or $[-100,100]$.  
    It maybe makes sense to use variables for the range.  
    The formulas are designed to fall in the range $[-100,100]$.  
    Thus scaling can be applied to obtain values in any appropriate range. 
    The scaling is denoted with the variable $k$.  The scale will be the same
    for all 5 elements.

    \subsection{ELEMENTS OF CRI}
        The CRI score consists of data collected from five
        different elements of an SDO.  
        \begin{enumerate}
            \item Quality
            \item Availability
            \item Satisfaction
            \item Schedule
            \item Requirements
        \end{enumerate}
        These five elements will be outline in the next sections.

@@

                The preferred method
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Scheduled Downtime + Unscheduled Downtime}}
                \]
                and the alternative method
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Unscheduled Downtime}}
                \]
                The only difference is the removal of scheduled downtime from 
                the calculation.  The calculation approach is typically specified in
                the contract associated with the SLA.  Thus, the Percent Uptime is important
                and it can either be supplied in the data or calculated from the 
                optional fields.

>>>>

    As long as those 5 features are met, the range of scores can be anything.  
    The range of $[-1,1]$ was chosen because it is easy to scale 
    to a different range such as $[-10,10]$ or $[-100,100]$.  
    Thus scaling can be applied to obtain values in any appropriate range. 
    The scaling factor is denoted with the variable $k$.  
    The scale must be the same
    for all 5 elements.

    \subsection{ELEMENTS OF CRI}
        Each of the 5 elements of CRI has its own set of data that needs to
        be collected and a formula for calculating a score. 
        These five elements will be outline in the next sections.

@@

                The preferred method:
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Scheduled Downtime + Unscheduled Downtime}}
                \]
                and the alternative method:
                \[
                    \text{Percent Uptime} = \frac{\text{Uptime}}{\text{Uptime + Unscheduled Downtime}}
                \]
                The only difference is the removal of scheduled downtime from 
                the calculation.  The calculation approach is typically specified in
                the contract associated with the SLA.  Thus, the Percent Uptime is important
                and it can either be supplied in the data or calculated from the 
                optional fields.
